### 2016-09-12 rebuttal.tex

should this be
\begin{quote}
The measure parameter of the simplify function lets the user specify the Python function used to determine how
\end{quote}
\begin{solution}
We have changed the sentence as suggested.
\end{solution}
\question Section 4.1
Should mpmath be cited here?

\begin{solution}
We have added a citation for mpmath.
\end{solution}
\end{questions}

\section{Reviewer 3}

\begin{questions}
\question I suggest a major rewrite of the paper, to improve the structure and group differently approached subjects. It would probably be best to:
\begin{enumerate}
\item Create a new section (following the introduction of SymPy) on projects that use SymPy, and put in it the materials currently available in supplement's sections 8, 9, 11. The comparison with Mathematica (supplement's section 10) should be moved either to the introduction as a section, or right after the introduction as its own section, but it should not be in the middle of the description of SymPy-powered projects.
\item  This should be followed by the list of SymPy packages and modules (currently section 3) and descriptions of selected modules (currently sections 3.1, 3.3, 3.5, supplement's sections 5, 7, and 9).
\item Now, basic usage can be given as its own section (currently done in sections 2.1 and 2.3), followed by introductions on usage of various modules (currently in sections 3.2, 3.4, 3.6, 4, 5, and supplement's sections 2, 3, 4, 6).
\item In-depth architecture (most of the so far unmentioned sections) can be given either as its own section, or made into a supplement of its own (as it is naturally far more technical and less interesting to general audience).
\item The current conclusion works fine as the finishing section of the paper.
\end{enumerate}
\begin{solution}
  FIXME.
  \begin{enumerate}
    \item I believe we shouldn't move ``Other Projects'' section to the
      main paper content.  It either should stay in the supplement or we
      should do a moderate cleanup for this section.  E.g. list only few
      projects here and put other in the supplement.  Or/And show here
      only project names.

    \item Logical place for above section - at the end of the
      paper, right before the "conclusion" section.

    \item We should either drop the Mathematica section or discuss
      other CAS too, which make this stuff suitable only as part
      of the suppliment.  I prefer the first variant.
  \end{enumerate}
\end{solution}
\end{questions}

### 2016-09-22 rebuttal.tex

\section{Reviewer 1}
\subsection{Basic reporting}
\begin{questions}
\question Generally good. A part that confused me is the assertion (footnote 3) that ``If
A and B are Symbols created with commutative=False then SymPy will keep A·B
and B·A distinct.'' Does that mean that BOTH of them must be created this way,
and that A and x (if x is created normally) will commute? Is there any way to
declare commutators? How does one guarantee that other pieces of code, e.g.
Gaussian elimination, respect non-commutativity?
\begin{solution}
  We have clarified the footnote. Both expressions must be set as
  \texttt{commutative=False}. Internally, in \texttt{Mul}, the ``commutative
  part'' of an expression is pulled out to the front and canonically ordered,
  and the ``noncommutative part'' is not reordered.

Commutators are implemented in the \texttt{sympy.physics.quantum} module and
are discussed in section 5.2.

Different algorithms do generally require special consideration for
noncommutative expressions to be correct. If an algorithm implicitly assumes
that expressions commute, it may return incorrect results when given a
noncommutative expression.
\end{solution}

\question References reasonable, though [8], an excellent reference, makes almost
precisely the opposite point to that for which it is cited --- ``simplification
is not well-defined''. I think the authors are trying to follow [8]'s
definition of simplification.
\begin{solution}
We agree that this is a bad reference, because we are not actually
using their definition.  Yes, that article rigorously defines
``simplification'', but it's just one approach.  This citation
was replaced with a better reference [28], that illustrates our point.
\end{solution}
\end{questions}

### 2016-09-22 rebuttal.tex

To avoid confusion, and to be consistent with the definitions used by the
official Python documentation, we have modified the manuscript to use
``submodule'' to refer to any module that is a dotted submodule of
\texttt{sympy}, such as \texttt{sympy.physics.quantum}. This is to emphasize
that these modules all live within the \texttt{sympy} namespace, as ``module''
can suggest a separate library.
\end{solution}

\question The sentences in lines 657--661 should swap places, because ``areas of mathematics'' are discrete mathematics, concrete mathematics, etc., while simplifying expressions, performing common calculus operations, pretty printing expressions, etc.\ belongs to common operations (``other areas'' is also fine, albeit slightly wrong).
\begin{solution}
The ``areas of mathematics'' was intended to encompass all mathematical
operations. We have rewritten the first sentence as
\begin{quote}
SymPy supports a wide array of mathematical facilities.
\end{quote}
We have also changed ``other included areas'' to ``other supported facilities'' in the third sentence.

The order of the subsequent sentences was chosen to match the order they were
presented in the paper, so we have left them as-is.
\end{solution}

\question In line 662 ``classical mechanics and quantum mechanics'' are listed as the only example of the support for specific domains, as in section 5, which leaves the impression that physics the only one. Either more domains should be listed, or it should be reworded to recognize the fact that there are no others.
\begin{solution}
Physics is a very wide subject, so it would be too rough a description to mention
it in the way you suggest, as a single domain.  Also, we list here only two of
the above mentioned
submodules in \texttt{sympy.physics}, but there are others.

### 2016-09-22 supplement.tex
Clarify "usage" of Sympy: that use -> that depend on
Ondrej (and perhaps Aaron) won't mention the Diofant project
among SymPy's users, so we must clarify that we mean by "using".
Add an intro sentence to the supplement, and re-arrange the paragraph
Grammar

@@

Section \ref{suppsec:Gruntz} discusses the Gruntz algorithm, used to
calculate limits in the SymPy.  Sections \ref{suppsec:Series}--\ref{suppsec:Ten}
discuss in depth some selected submodules.  Section \ref{suppsec:numsimpl}
discusses numerical simplification.  Section \ref{suppsec:examples} provides
additional examples for topics, discussed in the main paper.  In sections
\ref{sympy-gamma} and \ref{sympy-live} introduced the SymPy Gamma
and the SymPy Live projects.  Finally, section \ref{comp-mma} do
brief comparison of the SymPy with the Wolfram Mathematica and the
section \ref{other-proj} lists some projects that depend on SymPy.

@@

\section{Other Projects that Use SymPy}
\label{other-proj}
\input{other_projects_that_use_sympy}

>>>>

The supplementary material take a deeper look at certain topics in SymPy for
which there was not enough room to discuss in the paper.
Section \ref{suppsec:Gruntz} discusses the Gruntz algorithm, used to
calculate limits in the SymPy.  Sections \ref{suppsec:Series}--\ref{suppsec:Ten}
discuss in depth some selected submodules.  Section \ref{suppsec:numsimpl}
discusses numerical simplification.  Section \ref{suppsec:examples} provides
additional examples for topics, discussed in the main paper.  In sections
\ref{sympy-gamma} and \ref{sympy-live} the SymPy Gamma
and the SymPy Live projects are introduced.  Finally, section \ref{comp-mma} do
brief comparison of the SymPy with the Wolfram Mathematica and the
section \ref{other-proj} lists some projects that depend on SymPy.

@@

@@

\section{Other Projects that depend on SymPy}
\label{other-proj}
\input{other_projects_that_use_sympy}
